R for Clinical Study Reports and Submission

### 2022-03-19 submission-environment.Rmd

```{r, out.width="65%", echo=FALSE, fig.cap="cleanslate RStudio addin"}
knitr::include_graphics("images/cleanslate-addin.png")
```

>>>>

```{r, out.width="65%", echo=FALSE, fig.cap="cleanslate RStudio addin"}
# Web browser DevTools -> Print as PDF ->
# Edit PDF if necessary -> pdfcrop -> convert to PNG
knitr::include_graphics("images/cleanslate-addin.png")
```

### 2022-03-19 submission-package.Rmd

```{r, fig.cap="Preview the generated text file", out.width="100%", echo=FALSE}
knitr::include_graphics("images/preview-txt.png")
```

>>>>

```{r, fig.cap="Preview the generated text file", out.width="100%", echo=FALSE}
# Web browser DevTools -> Remove irrelevant elements ->
# Print as PDF -> Edit PDF if necessary -> pdfcrop -> convert to PNG
knitr::include_graphics("images/preview-txt.png")
```
